publications

### 2021-10-17 _posts/2021-09-29-nomorehugo/nomorehugo.Rmd
almost ready

I loved it at first. Relatively easy to set up, nice formatting, works on Rmarkdown. Lots of positives.

Some months passed, and I needed to update papers. Nothing too problematic, but; copying a folder, entering all of the pieces of information, and finally completing new entries always took longer than I would like. Compared to my CV in overleaf, I can add new presentations and papers in 30 seconds, easy.

Added to this, every time there was a non-trivial update to any of R, blogdown, Hugo, something with netlify, or some combination of the way these things interact tended to break everything. Not to mention the transition to wowchemy. Every time this happened, the "easiest" thing to do was to rebuild the entire site.

@@

One of the first things I read was that there were fewer dependencies on other things, including, including themes, hugo, and netlify.

@@

3. Adding altmertic badges is pretty easy, you can just add something like the following, copied from the [altmetric website](https://www.altmetric.com/products/altmetric-badges/)
<div data-badge-type="donut" data-doi="10.21105/joss.03041" data-hide-no-mentions="true" class="altmetric-embed"></div>

@@

<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>

>>>>

I loved it at first. Relatively easy to set up, nice formatting, works on Rmarkdown. Lots of positives. The documentation to get started is also pretty nice, and plenty of researchers have written their own tutorials.

But...

Some months passed, and I needed to update papers. Nothing too problematic, but; copying a folder, entering all of the pieces of information, and finally completing new entries always took longer than I would like. Compare this to my CV in overleaf, I can add new presentations and papers in 30 seconds, easy.

Worse, every time there was a non-trivial update to any of R, blogdown, Hugo, something with netlify, or some combination of the way these things interact tended to break everything. Not to mention the transition to wowchemy. Every time this happened, the "easiest" thing to do was to rebuild the entire site. In for a 10 minute update, out for hours of frustrations.

@@

One of the first things I read was that there were fewer dependencies on other things, including, including themes, hugo, and netlify. I put together this fairly simple site, and I lije it so far.

@@

3. Adding altmertic badges is pretty easy, you can just add something like the following, copied from the [altmetric website](https://www.altmetric.com/products/altmetric-badges/)
`<div data-badge-type="donut" data-doi="10.21105/joss.03041" data-hide-no-mentions="true" class="altmetric-embed"></div>`

<div data-badge-type="donut" data-doi="10.21105/joss.03041" data-hide-no-mentions="true" class="altmetric-embed"></div>

@@

`<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>`

### 2021-10-17 index.Rmd
almost ready

I’m a [Radboud Excellence Initiative](https://www.ru.nl/excellence/) Postdoctoral Research Fellow. I work in the [Lifespan Cognitive Dynamics Lab](https://www.rogierkievit.com/) based at the [Donders Institute](https://www.ru.nl/donders/). I did my DPhil in Experimental Psychology at the University of Oxford (a DPhil is a PhD but of course they need to call it something else)

@@

Radboud project

Open Scholarship - ReproducibiliTea and FORRT

I try to do my own small bit for the improvement of psychological science. Sometimes this is promoting open and reproducible research practices; others it is frustrating others by highlighting the importance of routinely estimating and reporting the reliability of our measurements. Mostly, I’d just like us all to get along and do good research.

Previous projects & talks

Seriousness - not a huge fan

I am happy to be contacted to discuss reliability of cognitive measures - particularly if you have questions about my splithalf package and need assistance with it.

(I try to keep this website up to date, however it may fall slightly behind. I do keep my [CV](Sam_Parsons_cv.pdf) up to date, so please do refer to that)

@@

Latest version: 0.8.1 “Rum Ham”

@@

![](splithalf.png)

>>>>

**About me** I’m a [Radboud Excellence Initiative](https://www.ru.nl/excellence/) Postdoctoral Research Fellow. I work in the [Lifespan Cognitive Dynamics Lab](https://www.rogierkievit.com/) based at the [Donders Institute](https://www.ru.nl/donders/). I did my DPhil in Experimental Psychology at the University of Oxford^[a DPhil is a PhD but of course they need to call it something else]

@@

**My current work** is focused on the reliability of longitudinal structural brain imaging data across brain regions, structural measures, and studies. My aim is to support developmental cognitive neuroscience study changes in brain structure and function by focusing on sources of reliability and error. My core approach will be based on intra-class effect decomposition, closely tied to generalisability theory. These models extract sources of variation in order to explore where the variation/error comes from in the model, moving beyond a single metric of reliability (e.g. ICC for test-retest). I believe it is important to support others who may want to use these approaches, so I will be dedicating time to share code and develop tutorials.

I am happy to be contacted to discuss reliability of cognitive measures - particularly if you have questions about my splithalf package (see below) and need assistance with it.

**Open Scholarship** I try to do my own small bit for the improvement of psychological science and open scholarship. Amy Orben, Sophia Cruwell, and I co-founded the [ReproducibiliTea Journal Clubs](https://reproducibilitea.org/) - now a large international community of Journal Clubs where folks talk about openness, reproducibility, and improving research practices. Flavio Azevedo and I also co-founded a [Framework for Open and Reproducible Research Training](https://forrt.org/) (FORRT), a pedagogy-focused community working to support those seeking to incorporate open and reproducible practices into their teaching and mentoring.

Eventually, I will get around to loading my previous projects & talks here. In the meantime, I have most of my talk slides on the [OSF](https://osf.io/rfy2h/), and you can check out my [CV](Sam_Parsons_cv.pdf). I do try to keep this website up to date, however it may fall behind my CV.

@@

Latest version: 0.8.1 “Rum Ham”^[Yes, all of the version names I have given the package are references to It's Always Sunny in Philadelphia. The pointlessness amuses me, and academia is often too serious, so count this as a minor act of rebellion]

@@

![](splithalf.png){ width=50% }

### 2021-10-17 papers.Rmd
almost ready

---
title: "papers"
site: distill::distill_article

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

aside_center <- function(text) {
  return(aside(center(list(text))))
}
```

## 2021

@@

@@

<div data-badge-type="donut" data-doi="10.21105/joss.03041" data-hide-no-mentions="true" class="altmetric-embed"></div>

<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>

@@

@@

## 2020

@@

@@

@@

@@

## 2019

@@

@@

@@

@@

@@

## 2018

@@

@@

## 2017

@@

@@

## 2016

@@

>>>>

---
title: "publications"
output:
  distill::distill_article:
    toc: true
    toc_depth: 3
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Peer-reviewed

### 2021

@@

<aside>
<div data-badge-type="donut" data-doi="10.1186/s40337-021-00444-2" data-hide-no-mentions="true" class="altmetric-embed"></div>
<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>
</aside>

@@

<aside>
<div data-badge-type="donut" data-doi="10.21105/joss.03041" data-hide-no-mentions="true" class="altmetric-embed"></div>
<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>
</aside>

@@

<aside>
<div data-badge-type="donut" data-doi="10.1080/02699931.2021.1915752" data-hide-no-mentions="true" class="altmetric-embed"></div>
<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>
</aside>

@@

<aside>
<div data-badge-type="donut" data-doi="10.3389/fpsyt.2021.622562" data-hide-no-mentions="true" class="altmetric-embed"></div>
<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>
</aside>

### 2020

@@

<aside>
<div data-badge-type="donut" data-doi="10.1007/s10802-020-00694-9" data-hide-no-mentions="true" class="altmetric-embed"></div>
<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>
</aside>

@@

<aside>
<div data-badge-type="donut" data-doi="10.1017/S0954579420000668" data-hide-no-mentions="true" class="altmetric-embed"></div>
<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>
</aside>

@@

<aside>
<div data-badge-type="donut" data-doi="10.1037/abn0000623" data-hide-no-mentions="true" class="altmetric-embed"></div>
<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>
</aside>

@@

<aside>
<div data-badge-type="donut" data-doi="10.1016/j.biopsycho.2020.107866" data-hide-no-mentions="true" class="altmetric-embed"></div>
<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>
</aside>

### 2019

@@

<aside>
<div data-badge-type="donut" data-doi="10.1002/acp.3628" data-hide-no-mentions="true" class="altmetric-embed"></div>
<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>
</aside>

@@

<aside>
<div data-badge-type="donut" data-doi="10.1177/2515245919879695" data-hide-no-mentions="true" class="altmetric-embed"></div>
<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>
</aside>

@@

<aside>
<div data-badge-type="donut" data-doi="10.1186/s40359-019-0342-8" data-hide-no-mentions="true" class="altmetric-embed"></div>
<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>
</aside>

@@

<aside>
<div data-badge-type="donut" data-doi="10.1027/2151-2604/a000387" data-hide-no-mentions="true" class="altmetric-embed"></div>
<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>
</aside>

@@

<aside>
<div data-badge-type="donut" data-doi="10.1037/abn0000406" data-hide-no-mentions="true" class="altmetric-embed"></div>
<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>
</aside>

### 2018

@@

<aside>
<div data-badge-type="donut" data-doi="10.1192/bjp.2018.43" data-hide-no-mentions="true" class="altmetric-embed"></div>
<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>
</aside>

@@

<aside>
<div data-badge-type="donut" data-doi="10.1007/s00426-018-1081-9" data-hide-no-mentions="true" class="altmetric-embed"></div>
<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>
</aside>

### 2017

@@

<aside>
<div data-badge-type="donut" data-doi="10.1038/s41562-018-0311-x" data-hide-no-mentions="true" class="altmetric-embed"></div>
<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>
</aside>

@@

<aside>
<div data-badge-type="donut" data-doi="10.1186/s40359-017-0210-3" data-hide-no-mentions="true" class="altmetric-embed"></div>
<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>
</aside>

### 2016

@@

<aside>
<div data-badge-type="donut" data-doi="10.5127/jep.053415" data-hide-no-mentions="true" class="altmetric-embed"></div>
<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>
</aside>

## Preprints and working papers

**Parsons, S** (2020). Exploring reliability heterogeneity with multiverse analyses: Data processing decisions unpredictably influence measurement reliability. Under review at Meta-Psychology. Preprint: [psyarxiv.com/y6tcz](https:/psyarxiv.com/y6tcz), data and code: [osf.io/haz6u/](https://osf.io/haz6u/)

FORRT. (2019). Introducing a Framework for Open and Reproducible Research Training (FORRT). (Co-author). Preprint: [osf.io/bnh7p/](https://osf.io/bnh7p/). Website: [forrt.org](https://forrt.org)

**Parsons, S** (2019). Visualising two approaches to explore reliability-power relationships. Preprint: [psyarxiv.com/qh5mf](https://psyarxiv.com/qh5mf)
